Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-18 code-tests.tex
first crack at section on code comparisons.

@@

@@

After the test problems are selected by the test runner script, they
are run in succession either by with \enzo\ executable contained within
that distribution or an external executable built from another version
and specified by the user.  This allows for any version of the code to
be tested with an identical set of test problems.  After running the
test problem simulations, the test runner then performs a series of
basic analysis tasks using the \texttt{yt} analysis toolkit
\citep{2011ApJS..192....9T, 2011arXiv1112.4482T}.  The default
analysis performed on all test problems includes calculation of
various statistics, such as extrema; mean; and variance, on the fields
present in the output data.  Custom analysis provided by scripts that
accompany the test problem parameter files is run for special cases,
such as when an analytical solution exists that can be compared
against the simulation data.  After the analysis is performed, the
results are compared against a set of gold standard results which are
maintained on a website and downloaded on the fly by the test runner
script.  Alternately, results from any version of \enzo\ can be stored
locally and compared to any other version of the code.  Below, we
describe some of the key test problems which are used to verify proper 
behavior.

\red{(Brian)} Refer to all code comparisons that Enzo has been part of.

>>>>

Ensuring that a complex piece of software is behaving correctly is a
non-trivial task.  While there are a range of techniques that one can
apply to ensure correctness, the \enzo\ code uses two primary methods:
a suite of test problems that can be compared to previous versions of
the code, to ensure that \enzo\ is, e.g., running correctly on a new
computer, with a new compiler, or after substantial changes have been
made to the code base; and by direct comparisons to other
astrophysical fluid dynamics codes.  We describe the \enzo\ test
methodology in Section~\ref{sec.tests.suite}, code comparisons in
Section~\ref{sec.tests.compare}, and show a small set of
representative test problems in Section~\ref{sec.tests.problems}.

@@

\subsubsection{The \enzo\ test suite}
\label{sec.tests.suite}

@@

After the test problems are selected by the test runner script, they
are run in succession either by with \enzo\ executable contained
within that distribution or an external executable built from another
version and specified by the user.  This allows for any version of the
code to be tested with an identical set of test problems.  After
running the test problem simulations, the test runner then performs a
series of basic analysis tasks using the \texttt{yt} analysis toolkit
\citep{2011ApJS..192....9T, 2011arXiv1112.4482T}.  The default
analysis performed on all test problems includes calculation of
various statistics, such as extrema; mean; and variance, on the fields
present in the output data.  Custom analysis provided by scripts that
accompany the test problem parameter files is run for special cases,
such as when an analytical solution exists that can be compared
against the simulation data.  After the analysis is performed, the
results are compared against a set of gold standard results which are
maintained on a website and downloaded on the fly by the test runner
script.  Alternately, results from any version of \enzo\ can be stored
locally and compared to any other version of the code.  In
Section~\ref{sec.tests.problems}, we describe some of the key test
problems which are used to verify proper behavior.  All of these test
problems, as well as the scripts to generate the figures from them,
are available in the \enzo\ test suite.

\subsubsection{Code comparisons}
\label{sec.tests.compare}

Over the course of its existence, \enzo\ has been involved in several
comparisons with other astrophysical codes used for self-gravitating
fluid dynamics.

Cosmology: 
Santa Barbara Clusters, \citep{SantaBarbara}.
Enzo-gadget cosmology comparison, \citep{2005ApJS..160....1O}.
Regan et al. Enzo/Gadget Lyman Alpha Forest comparison,
\citep{2007MNRAS.374..196R}.
Heitmann n-body comparison, \citep{2008CS&D....1a5003H}

Hydro:
Agertz hydro comparison, \citep{2007MNRAS.380..963A}.
Tasker test suite, \citep{Tasker2008}.

Turbulence:
Kritsuk supersonic MHD turbulence comparison,
\citep{2011ApJ...737...13K}.  Compares MHD-CT version.

Radiation transport:
Iliev et al. radiation transport comparison, paper II,
\citep{IlievEtAl2009}.  Compares enzo-FLD.
